Minimal Positive Influence of Helpline Efforts on Reduction of Homeless Death in Toronto

### 2024-03-12 paper/paper.qmd
Added rationalization of existence for model 2 in model section
Added material to result and discussion section

```{r}
#| label: tbl-monthly-coded
#| tbl-cap: Sample of monthly summation for Helpline Coded Calls data
#| echo: false
#| warning: false

@@

@@

@@

## Realistic Interpretation of Net Efforts

-   On average, for every increase in calls coded by the helpline, there
    is a 0.0003 unit decrease in homeless death in Toronto. There is an
    overall reduction, albeit very small, in homeless death as the
    number of total coded calls increase. This implies that the helpline
    need to take at minimum 3333 calls per month to save 1 homeless life
    in Toronto. On average, the helpline takes 14828.59 calls per month,
    meaning that 4.45 lives are saved on average.
-   4.45 is not a significant number in both a practical and statistical
    sense. To improve the return on total number of calls coded, we
    attempted to identify promising call codes that contribute to the
    net positive reduction in homeless death. Out of the 13 different
    call codes, *Referral to Shelter* and *Information on Homeless
    Prevention* are best suited as individual efforts of measurement for
    positive impacts because they provide a count of the number of
    callers provided with directions or advice.

## Individual Effort: Referral to Shelter

-   On average, for every homeless caller referred to shelter, there is
    a 0.0059 unit **increase** in homeless death in Toronto. Though not
    significant on a statistical level, this trend is still very
    counter-intuitive discouraging. In the case where the correlation is
    more significant, we would want to further analyze factor related to
    referrals to shelter. Accuracy on the current status of shelters,
    level of detail on instructed, and misjudgment of shelter
    eligibility are possible factors of examination. However, since the
    effect of this call code is statistically insignificant, it is more
    likely just a fluke caused by the dataset.

## Individual Effort: Information on Homelessness Prevention

>>>>

```{r}
#| label: tbl-monthly-coded
#| tbl-cap: Sample of monthly summation for Helpline Coded Calls data
#| echo: false
#| message: false

@@

The Total Coded model estimates the the total helpline efforts against
Toronto's homeless death count.

@@

In case of oversimplification, a second model is proposed to isolate the
effects of calls that refer individuals to shelter and calls that
provide information on homelessness prevention.

@@

## Interpretation of Efforts

-   On average, for every increase in calls coded by the helpline, there
    is a 0.0003 unit decrease in homeless death in Toronto. There is an
    overall reduction, albeit very small, in homeless death as the
    number of total coded calls increase. This implies that the helpline
    need to take at minimum 3333 calls per month to save 1 homeless life
    in Toronto. On average, the helpline takes 14828.59 calls per month,
    meaning that 4.45 lives are saved on average.
-   4.45 is not a significant number in both a practical and statistical
    sense. To improve the return on total number of calls coded, we
    attempted to identify promising call codes that contribute to the
    net positive reduction in homeless death. Out of the 13 different
    call codes, *Referral to Shelter* and *Information on Homeless
    Prevention* are best suited as individual efforts of measurement for
    positive impacts because they provide a count of the number of
    callers provided with directions or advice.
-   On average, for every homeless caller referred to shelter, there is
    a 0.0059 unit **increase** in homeless death in Toronto. Though not
    significant on a statistical level, this trend is still very
    counter-intuitive discouraging. In the case where the correlation is
    more significant, we would want to further analyze factor related to
    referrals to shelter. Accuracy on the current status of shelters,
    level of detail on instructed, and misjudgment of shelter
    eligibility are possible factors of examination. However, since the
    effect of this call code is statistically insignificant, it is also
    likely to be just a fluke of observation.
-   For every caller provided with information on homeless prevention
    information, there is an average decrease of 0.0048 death count in
    Toronto.

## Implication of Insignificance: More Qeustions than Answers

-   Homeless life is not easy, data shows that a total of 522 homeless
    individual died in Toronto between November 2020 to June 2023.

-   The Central Intake Line is created with the intend to help homeless
    individuals in need. It provides a 24/7 platform for individuals to
    receive government help.

-   The insignificance of its influence suggests that the helpline has
    not fulfilled its intended purpose, though it is also important to
    note that having insignificant effect on reducing death count does
    not mean the helpline has not contributed to the well-being of
    Toronto's homeless population in other ways.

-   This makes us question
